Processing of visual and non-visual naturalistic spatial information in the "parahippocampal place area"

### 2021-02-15 paper/main.tex
minor cleaning

\noindent Supplemental Material
\begin{itemize}
    \item discuss differences of contrasts (s. Simons comment)?
\end{itemize}

@@

\begin{itemize}
    \item https://www.springernature.com/gp/authors/research-data-policy/data-availability-statements/12330880i
    \item cf. other Scienctific Data analysis paper
\end{itemize}

@@

\begin{figure*}[h!]
\centering
    \includegraphics[width=\linewidth]{figures/regressor-corr} \caption{Pearson
        correlation coefficients of modeled time series used as regressors in
        the GLM analysis of the
        audio-description (blue; see Table \ref{tab:ao-events} for a
        description) and audio-visual movie (red; see Table
        \ref{tab:av-events}).
        Values are rounded to the nearest tenth.
        The correlation between the two stimuli's
        root mean square volume and between their left-right difference in
        volume yielded the highest correlation values
        (\texttt{fg\_ad\_rms} and \texttt{fg\_av\_ger\_rms}, r=.7635;
        \texttt{fg\_ad\_lrdiff} and \texttt{fg\_av\_ger\_lrdiff}, r=.7749).
        \todo[inline]{checked it, all labels listed}
      }
\label{fig:reg-corr}
\end{figure*}

@@

% PPA: intro
First, we analyzed data from the movie offering ecologically more valid visual
stimulation.
%
An early study \citep{bartels2004mapping} that manually annotated the content of
movie frames (color, faces, language, and human bodies) found that
specialization of functional areas is preserved during movie watching.
%
Contrary to \citep{bartels2004mapping} who annotated the content of movie
frames, we categorized each frame after a cut independent of its specific
content  \todo{Bartels' clusters are actually pretty big too}
% exploited cinematographic tendencies
exploiting a cinematographic confound in the stimulus structure (cf. section
\ref{rationale}):
% establishing shots vs. e.g. over-the-shoulder shots
film directors tend to establish the geometry of locations earlier in the movie
and tend to later focus more on persons and objects relevant to the evolved plot
\citep{brown2012cinematography, mercado2011filmmakers}.
% hypo
Despite our ad hoc approach, we hypothesized that confounding variables would
average out, and our whole-brain analyses would lead to significant clusters in
the PPA.
% results
Group results of the AV stimulus' primary contrast yielded one cluster that
spans the group overlap of individual PPA ROIs from anterior to posterior.
% confound of higher perception
The cluster's extension into more posterior, early visual areas can be
attributed to the averaging process that did not control for confounding visual
features.
% solution
Thus to control confounding variables, future studies that aim to use a movie to
localize visual areas in individual subjects should extensively annotate the
content of frames (e.g.  using the open-source solution ``Pliers'' for feature
extraction from a visual naturalistic stimulus; \citep{mcnamara2017developing}).
% we took advantage of cinematography
We here took advantage of an idiosyncrasy of movie directing to shift from
depicting the spatial layout to to later depicting persons and objects.
% know your stimulus
Given that this shift is common in movies, investigators should be aware that
cinematographic tendencies are part of movie's confound structure that might,
depending on the research question, influence the results.
% conclusion
In summary, results from the visual localizer paradigm using blocks of pictures
generalize to an ad hoc approach to operationalize the perception of spatial
information at the moment of cuts in an audio-visual movie.

@@

\todo[inline]{scientific data has no conclusion -> last paragraph}
\todo[inline]{(2nd part of) following paragraph pretty similar to discussion's
first paragraph}
% natural stimulation
In summary, natural stimuli like movies \citep{eickhoff2020towards,
hasson2008neurocinematics, sonkusare2019naturalistic} or narratives
\citep{hamilton2018revolution, honey2012not, lerner2011topographic,
silbert2014coupled, wilson2008beyond} offer an easy to implement, continuous,
complex, immersive, task-free paradigm that more closely resembles our natural
dynamic environment than traditional experimental paradigms.
% method
We took advantage of three fMRI datasets and two stimulus annotations that are
part of the studyforrest dataset
\href{http://www.studyforrest.org}{studyforrest.org} to operationalize the
perception of spatial information embedded an audio-visual movie and an auditory
narrative, and compare current results to results gained from a traditional
visual localizer.
% results
In general, results add evidence that a model-driven GLM analysis based on
annotations can be run on data from naturalistic stimuli to localize concise
functional areas and networks correlating with specific perceptual processes.
% interpretation
More specifically, our results demonstrate that increased activation in the PPA
during the perception of static pictures generalizes to the perception of
spatial information embedded in a movie and an exclusively auditory stimulus.
% interpretation: aPPA vs. pPPA
Further, our results provide evidence that the PPA can be divided into
functional subregions that [might] work together during the perception of visual
scenes.
% interpretation
Lastly, a naturally engaging auditory narrative might - in principle -
substitute a visual paradigm to localize the anterior part of the PPA in
subjects who are not [willing or] able to follow task instructions during brain
scanning.

@@

\todo[inline]{Figures \& Tables have their own section, the editor puts them
where he wants them?}

@@

\todo[inline]{discuss results in light of ``negative control'' (-> definition \&
purpose}

@@

The four control contrasts of the AV stimulus that compared the
\texttt{no\_cuts} to categories of movie cuts all lead to null results.
% AD anno in AV data
The AV contrast using nouns (\texttt{se\_new} > \texttt{se\_old}): PPA
(unilateral), LOC (bilateral); These noun categories show highest correlation
among nouns with their cut counterpart \texttt{se\_new} (nouns) is r$\approx$0.3
correlated with \texttt{vse\_new} (cuts); \texttt{se\_old} (nouns) is
r$\approx$0.4 correlated with \texttt){vse\_old}.

>>>>

\noindent Supplemental Material
\begin{itemize}
    \item more detailed discussion differences of contrasts (s. Simons comment)?
    \item discussion of control contrasts
\end{itemize}

@@

\begin{itemize}
    \item https://www.springernature.com/gp/authors/research-data-policy/data-availability-statements/12330880i
    \item cf. other Scientific Data analysis paper
\end{itemize}

@@

\begin{figure*}[h!]
\centering
    \includegraphics[width=\linewidth]{figures/regressor-corr} \caption{Pearson
        correlation coefficients of modeled time series used as regressors in
        the GLM analysis of the
        audio-description (blue; see Table \ref{tab:ao-events} for a
        description) and audio-visual movie (red; see Table
        \ref{tab:av-events}).
        Values are rounded to the nearest tenth.
        The correlation between the two stimuli's
        root mean square volume and between their left-right difference in
        volume yielded the highest correlation values
        (\texttt{fg\_ad\_rms} and \texttt{fg\_av\_ger\_rms}, r=.7635;
        \texttt{fg\_ad\_lrdiff} and \texttt{fg\_av\_ger\_lrdiff}, r=.7749).
      }
\label{fig:reg-corr}
\end{figure*}

@@

% PPA: intro
First, we analyzed data from the movie offering ecologically more valid visual
stimulation.
%
An early study \citep{bartels2004mapping} that manually annotated the content of
movie frames (color, faces, language, and human bodies) found that
specialization of functional areas is preserved during movie watching.
\todo{clusters are pretty big too}
%
Contrary to \citep{bartels2004mapping} who annotated the content of movie
frames, we categorized each frame after a cut independent of its specific
content
% exploited cinematographic tendencies
exploiting a cinematographic confound in the stimulus structure (cf. section
\ref{rationale}):
% establishing shots vs. e.g. over-the-shoulder shots
film directors tend to establish the geometry of locations earlier in the movie
and tend to later focus more on persons and objects relevant to the evolved plot
\citep{brown2012cinematography, mercado2011filmmakers}.
% hypo
Despite our ad hoc approach, we hypothesized that confounding variables would
average out, and our whole-brain analyses would lead to significant clusters in
the PPA.
% results
Group results of the AV stimulus' primary contrast yielded one cluster that
spans the group overlap of individual PPA ROIs from anterior to posterior.
% confound of higher perception
The cluster's extension into more posterior, early visual areas can be
attributed to the averaging process that did not control for confounding visual
features.
% solution
Thus to control confounding variables, future studies that aim to use a movie to
localize visual areas in individual subjects should extensively annotate the
content of frames (e.g.  using the open-source solution ``Pliers'' for feature
extraction from a visual naturalistic stimulus; \citep{mcnamara2017developing}).
% we took advantage of cinematography
We here took advantage of an idiosyncrasy of movie directing to shift from
depicting the spatial layout to to later depicting persons and objects.
% know your stimulus
Given that this shift is common in movies, investigators should be aware that
cinematographic tendencies are part of movie's confound structure that might,
depending on the research question, influence the results.
% conclusion
In summary, results from the visual localizer paradigm using blocks of pictures
generalize to an ad hoc approach to operationalize the perception of spatial
information at the moment of cuts in an audio-visual movie.

@@

\todo[inline]{scientific data has no conclusion -> last paragraph}
% natural stimulation
In summary, natural stimuli like movies \citep{eickhoff2020towards,
hasson2008neurocinematics, sonkusare2019naturalistic} or narratives
\citep{hamilton2018revolution, honey2012not, lerner2011topographic,
silbert2014coupled, wilson2008beyond} offer an easy to implement, continuous,
complex, immersive, task-free paradigm that more closely resembles our natural
dynamic environment than traditional experimental paradigms.
% method
We took advantage of three fMRI datasets and two stimulus annotations that are
part of the studyforrest dataset
\href{http://www.studyforrest.org}{studyforrest.org} to operationalize the
perception of spatial information embedded an audio-visual movie and an auditory
narrative, and compare current results to results gained from a traditional
visual localizer.
% results
In general, results add evidence that a model-driven GLM analysis based on
annotations can be run on data from naturalistic stimuli to localize concise
functional areas and networks correlating with specific perceptual processes.
% interpretation
More specifically, our results demonstrate that increased activation in the PPA
during the perception of static pictures generalizes to the perception of
spatial information embedded in a movie and an exclusively auditory stimulus.
% interpretation: aPPA vs. pPPA
Further, our results provide evidence that the PPA can be divided into
functional subregions that [might] work together during the perception of visual
scenes.
% interpretation
Lastly, a naturally engaging auditory narrative might - in principle -
substitute a visual paradigm to localize the anterior part of the PPA in
subjects who are not [willing or] able to follow task instructions during brain
scanning.

@@

\todo[inline]{Figures \& Tables have their own section??? the editor puts them
where he wants them?}

@@

\todo[inline]{discuss results in light of ``negative control'' (-> definition \&
purpose)}

@@

The four control contrasts of the AV stimulus that compared the
\texttt{no\_cuts} to categories of movie cuts all lead to null results.
% AD anno in AV data
The AV contrast using nouns (\texttt{se\_new} > \texttt{se\_old}): PPA
(unilateral), LOC (bilateral); These noun categories show highest correlation
among nouns with their cut counterpart \texttt{se\_new} (nouns) is r$\approx$0.3
correlated with \texttt{vse\_new} (cuts); \texttt{se\_old} (nouns) is
r$\approx$0.4 correlated with \texttt{vse\_old}.
